---
title: "ST Analysis: Doctorates"
output: html_document
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(knitr)
library(kableExtra)
library(tidyverse)
```


<!-- Nav tabs -->
<ul class="nav nav-tabs" id="myTab" role="tablist">
  <li class="nav-item">
    <a class="nav-link active" id="stats-tab" data-toggle="tab" href="#stats" role="tab" aria-controls="stats" aria-selected="false">Descriptive statistics</a>
  </li>
  <li class="nav-item">
    <a class="nav-link" id="anal-sum-tab" data-toggle="tab" href="#anal-sum" role="tab" aria-controls="anal-sum" aria-selected="false">Analysis Summary</a>
  </li>
  <li class="nav-item">
    <a class="nav-link" id="gpa-tab" data-toggle="tab" href="#gpa" role="tab" aria-controls="gpa" aria-selected="false">GPA: Linear Regression</a>
  </li>
  <li class="nav-item">
    <a class="nav-link" id="sep-tab" data-toggle="tab" href="#sep" role="tab" aria-controls="sep" aria-selected="false">Separation: Logistic Regression</a>
  </li>
  <li class="nav-item">
    <a class="nav-link" id="ttd-tab" data-toggle="tab" href="#ttd" role="tab" aria-controls="ttd" aria-selected="false">Time-to-Degree: Survival Analysis</a>
  </li>
  <li class="nav-item">
    <a class="nav-link" id="urm-tab" data-toggle="tab" href="#urm" role="tab" aria-controls="urm" aria-selected="false">URM: Logistic Regression</a>
  </li>
  <li class="nav-item">
    <a class="nav-link" id="gender-tab" data-toggle="tab" href="#gender" role="tab" aria-controls="gender" aria-selected="false">Gender: Logistic Regression</a>
  </li>
  <li class="nav-item">
    <a class="nav-link" id="prev-tab" data-toggle="tab" href="#prev" role="tab" aria-controls="prev" aria-selected="false">Previous Degree: Logistic Regression</a>
  </li>
  
</ul>

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_dat5 <- read.xlsx("doc_dat5.xlsx")
doc_dat5_stem <- filter(doc_dat5, STEM == 1)
doc_dat5_non_stem <- filter(doc_dat5, STEM == 0)

doc_dat6 <- read.xlsx("doc_dat6.xlsx")
doc_dat6_stem <- filter(doc_dat6, STEM == 1)
doc_dat6_non_stem <- filter(doc_dat6, STEM == 0)

```

<!-- Tab panes -->
<div class="tab-content" id="myTabContent">
  <div class="tab-pane fade" id="stats" role="tabpanel" aria-labelledby="stats-tab">

# {.tabset}

## All Doctorates

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_summary <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'stats')
kable(doc_summary, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```


## STEM

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_stem_summary <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'stats_s')
kable(doc_stem_summary, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```


## Non-STEM

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_non_stem_summary <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'stats_n')
kable(doc_non_stem_summary, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```

  </div>


  <div class="tab-pane fade" id="anal-sum" role="tabpanel" aria-labelledby="anal-sum-tab">

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_anal_sum <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'summary')
kable(doc_anal_sum, format = "html", caption = "Coefficient for linear regression, 
                          marginal effect for logistic regression, 
                          hazard ratio for survival analysis
                          (p-value in parentheses)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```

  </div>


  <div class="tab-pane fade" id="gpa" role="tabpanel" aria-labelledby="gpa-tab">


# {.tabset}

## Year 1

### All Doctorates

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_gpa1_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'gpa1')
kable(doc_gpa1_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```


### STEM

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_stem_gpa1_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'gpa1_s')
kable(doc_stem_gpa1_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```

### Non-STEM

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_non_stem_gpa1_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'gpa1_n')
kable(doc_non_stem_gpa1_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```

## Year 2

### All Doctorates

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_gpa2_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'gpa2')
kable(doc_gpa2_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```


### STEM

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_stem_gpa2_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'gpa2_s')
kable(doc_stem_gpa2_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```

### Non-STEM

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_non_stem_gpa2_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'gpa2_n')
kable(doc_non_stem_gpa2_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```

  </div>

  <div class="tab-pane fade" id="sep" role="tabpanel" aria-labelledby="sep-tab">


# {.tabset}

## Year 1

### All Doctorates

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_sep1_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'sep1')
kable(doc_sep1_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```


### STEM

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_stem_sep1_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'sep1_s')
kable(doc_stem_sep1_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```

### Non-STEM

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_non_stem_sep1_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'sep1_n')
kable(doc_non_stem_sep1_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```

## Year 2

### All Doctorates

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_sep2_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'sep2')
kable(doc_sep2_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```


### STEM

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_stem_sep2_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'sep2_s')
kable(doc_stem_sep2_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```

### Non-STEM

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_non_stem_sep2_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'sep2_n')
kable(doc_non_stem_sep2_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```
  
  </div>
  
  <div class="tab-pane fade" id="ttd" role="tabpanel" aria-labelledby="ttd-tab">

# {.tabset}
  
## All Doctorates

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_ttd_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'ttd')
kable(doc_ttd_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```


## STEM

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_stem_ttd_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'ttd_s')
kable(doc_stem_ttd_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```

## Non-STEM

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_non_stem_ttd_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'ttd_n')
kable(doc_non_stem_ttd_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```

  </div>
  
  <div class="tab-pane fade" id="urm" role="tabpanel" aria-labelledby="urm-tab">

# {.tabset}
  
## All Doctorates

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_urm_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'urm')
kable(doc_urm_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```


## STEM

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_stem_urm_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'urm_s')
kable(doc_stem_urm_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```

## Non-STEM

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_non_stem_urm_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'urm_n')
kable(doc_non_stem_urm_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```

  </div>
  
  <div class="tab-pane fade" id="gender" role="tabpanel" aria-labelledby="gender-tab">

# {.tabset}
  
## All Doctorates

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_gender_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'gender')
kable(doc_gender_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```


## STEM

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_stem_gender_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'gender_s')
kable(doc_stem_gender_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```

## Non-STEM

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_non_stem_gender_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'gender_n')
kable(doc_non_stem_gender_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```
  
  </div>
  
  <div class="tab-pane fade" id="prev" role="tabpanel" aria-labelledby="prev-tab">

# {.tabset}
  
## All Doctorates

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_prev_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'prev')
kable(doc_prev_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```


## STEM

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_stem_prev_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'prev_s')
kable(doc_stem_prev_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```

## Non-STEM

```{r message=FALSE, warning=FALSE, echo=FALSE}

doc_non_stem_prev_model_summary_df <- read.xlsx("Doc_Complete Summaries.xlsx", sheet = 'prev_n')
kable(doc_non_stem_prev_model_summary_df, format = "html", caption = "") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  column_spec(2, width = "3cm")

```

  </div>
</div>




